\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-07-14 article.tex
Added text to the introduction and tags section

% Introduction
%   Definitions
%     Patterns
%     Fundamental movements
%  Related work
%  Problem statement
%     Groups of techniques
%       blocks
%       strikes
%       thrusts
%       punches
%     Tagging

% Method
%   Approach
%   Collecting data
%   Analysis of data
%   Tagging
%     Group of tags || Kind of Tags
%       height
%       weapon
%       type etc.
%    Difficulties related to tagging
%  Uncertainty
%
% Results
%   Tables
%   Graphs
% Conclusion

%Related work
%  Right Leg Bias

@@

  A \emph{pattern} in International Taekwon-Do Federation (ITF) is defined as
  a choreographed sequence of fundamental movements. These \emph{fundamental
  movements} are basic elements which represent an attack or defense towards a
  specific target area, or a predetermined action of an attacker.

  Combined in a pattern, it allows the student to systematically deal with one
  or several imaginary opponents under various assumptions, using every
  available attacking and blocking tool from different directions. In
  addition, the techniques should also be evenly distributed between the left
  and the right side\cite{cyclo:vol1}.

  It has, however, recently been observed that a bias towards the right leg
  exist\cite{rlb}. % ALL patterns..

% how is related work written about?

% recent studies of a right leg bias; Recent work has found that..
%
% in this paper, therefore, we analyze..

%It has, however, recently been observed that a right leg bias
%exist\cite{rlb} when looking at all the 24 Taekwon-Do patterns.

% Is there a bias towards the *right* leg in Chon-Ji to Juche?

%A study of arm techniques in patterns Chon-Ji to Juche, initiated in the hope
%of uncovering whether or not there is a bias to either arm, is reported here.

% Problem Statement
%
% pp. 154-155
%
% The following points should be considered while performing patterns:
%
%   9. Attack and defense techniques should be equally
%      distributed among right and left hands and feet
%
%
%
% and the recent discovery of the right leg bias,
%
% Is there a bias towards the right or the left arm in ITF Taekwon-Do
% patterns Chon-Ji to Juche?
%
% note that Gibb's article includes *all* the patterns

%Overall, there are a total of 152 kicks. 85 kicks are with the right
%leg, and 67 kicks are with the left leg. This means that 56\% of all
%kicks in patterns are with the right leg, whereas 44\% are with the left
%leg.

\Section{Method}

How did you go about solving or making progress on the problem? Did you
use simulation, analytic models, prototype construction, or analysis of
field data for an actual product? What was the extent of your work (did
you look at one application program or a hundred programs in twenty
different programming languages?) What important variables did you
control, ignore, or measure?

% Tagging can be defined as the practice of creating and
% managing labels that categorize content using simple
% keywords.

@@

What's the answer? Specifically, most good computer architecture papers
conclude that something is so many percent faster, cheaper, smaller, or
otherwise better than something else. Put the result there, in numbers.
Avoid vague, hand-waving results such as ``very'', ``small'', or
``significant.''

If you must be vague, you are only given license to do so when you can
talk about orders-of-magnitude improvement. There is a tension here in
that you should not provide numbers that can be easily misinterpreted,
but on the other hand you don't have room for all the caveats.

@@

What are the implications of your answer? Is it going to change the
world (unlikely), be a significant ``win'', be a nice hack, or simply
serve as a road sign indicating that this path is a waste of time (all
of the previous results are useful). Are your results general,
potentially generalizable, or specific to a particular case?

@@

  % Odd-Magne Hansen for helping me with the terminology, and general feedback
  Todo.

@@

@@

>>>>

% Method
%   Analysis of data || Processing
%    Difficulties related to tagging
%  Uncertainty
%
% Results
%   Tables
%   Graphs
% Conclusion

@@

  A \emph{pattern} in International Taekwon-Do Federation (ITF) is defined as
  a choreographed sequence of fundamental movements. These \emph{fundamental
  movements} are basic elements which represent an attack or defense against a
  specific target area, or a predetermined action of an attacker.

  Combined in a pattern, it allows the student to systematically deal with one
  or several imaginary opponents under various assumptions, using every
  available attacking and blocking tool from different directions.
  Furthermore, the techniques should also be evenly distributed between the
  left and the right side\cite{cyclo:vol1}.

  It has, however, recently been observed that a bias towards the right leg
  exist. The study by Gibbs\cite{rlb} show that there is a total of 152 kicks
  in patterns Chon-Ji to Tong-Il. 85 kicks are with the right leg, and 67
  kicks are with the left leg. This means that 56\% of the kicks are with the
  right leg, and 44\% with the left leg.

  The work by Gibbs focused on kicks in all patterns, whereas this article
  examines patterns Chon-Ji to Juche. Looking at kicks in said patterns using
  Gibbs' paper, we find that there are 72 kicks in total. 42 kicks are with
  the right leg, and 30 kicks are with the left leg. Roughly 58\% of the kicks
  are with the right leg, and about 42\% with the left. Thus, the right leg
  bias still holds.

  In this article, therefore, we analyze hand techniques in patterns Chon-Ji
  to Juche using tags and report our findings of a left arm bias.

\SubSection{Tags and Tagging}

%   Applying tags (to dataset)
%   Tagging
%     Group of tags
%     Groups of techniques {blocks, strikes, thrusts, punches}
%       height
%       weapon
%       type etc.

  In a hierarchical and exclusive classification system, each object belong in
  one unambiguous category, which in turn is within another more general one.
  Take the hierarchy of folders in a computer file system, for example. If we
  want to organize articles on birds native to Africa in a directory, we have
  several options:

  \begin{lstlisting}
    1. ~/articles/birds
    2. ~/articles/africa
    3. ~/articles/africa/birds
    4. ~/articles/birds/africa
  \end{lstlisting}

  all articles on birds
  all articles on africa
  all articles on african birds
  all articles on birds from africa

  How we choose to organize the folders reflects a decision concerning the
  relative importance of each characteristic\cite{golder:ct}. Folder names and
  levels are in themselves informative, in that, like tags, they describe the
  information held within them\cite{jones:folders}.

% go through different folder setup
% then insert the text about ``Tags, on the other hand..''
% elaborate what it means that an object can have many tags
% show a venn diagram
% explain the venn diagram

  Tags, on the other hand, are \emph{non-hierarchical} and \emph{inclusive},
  which is to say that an object can be associated with a great variety of
  tags simultaneously\cite{golder:ct}.

  % Finally we can define tags as being non-hierarchical..
  \emph{Tags} are non-hierarchical descriptive terms, keywords or labels that
  is attached to an object for later
  retrieval\cite{golder:ct}\cite{huang:tt}\cite{shirky:ontology}\cite{wikipedia:tags}.

  %(mention polyhierarchical from the IA book)

  %Descriptive terms, keywords or labels are metadata associated with a given
  %object used to describe a concept or type of information\cite{heymann:ccch}.

  %Object.. (define an object, then say that in this article an object is a
  %pattern movement || a movement in a pattern)

  %Later retrieval..

% what does this all mean?
%   non-hierarchical
%   descriptive terms, keywords or labels
%   object (a movement in a pattern)

% Why do we tag?
%   this kind of metadata helps describe an item
%   allows it to be found again by searching
%   future navigation, filtering or search
%   later retrieval
%   categorize content using keywords
%   grouping related objects
%   classifies
%   organize
%   for the purpose of classification and retrieval
% How do we tag (tagging)?
%   define tagging

%\emph{Tagging} can be defined as the practice of creating and managing labels
%that categorize content using simple keywords

Tagging is the act of organizing a collection of entities, whether things or
concepts, into related groups\cite{shirky:ontology}.

\Section{Method}
  Write introduction.

% Three parts
%   1. terminology (sonkal.taekwondo.cz)
%   2. english description (condensed encyclopedia)
%   3. tagging (how is tagging used? what is its role?)

\SubSection{The Data}

  Our data comes from two different sources. The terminology associated with
  movements are from Taekwon-Do ITF Sonkal
  Praha\footnote{\url{http://sonkal.taekwondo.cz}}, and the English
  description of each movement is from the condensed
  encyclopedia\cite{cyclo:con}.

\SubSection{Approach}
% collecting data

  Todo.

% registered terminology to all pattern movements, grouped by pattern names, including their pattern movement number, and motion type (normal, slow, etc.), link to movements_all.txt ?
%   reviewed the terminology and movement type with odd-magne using a wiki
%   made a few changes (corrected terminology for punch for instance)
% added english description from the condensed encyclopedia to pattern
%   checked that the terminology corresponded to the actual pattern movement
% added tags
%   (documented the tagging process)
%   give an overview over (groups of) tags, see movements_with_tags.txt
% divided each pattern into its own text file
% modelled the project in the database (./models)
%   explain all attributes etc.
% made a ruby script to parse the text files (link to bootstrap.rb ?)
%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
%   saving the data into an sqlite3 database for analysis
%
% show an example (chon-ji movement no. 1, for instance)
%
%
%
% The terminology to all pattern movements where first inserted into a text
% file, along with.. || including..
%

% hva forholder jeg meg til ved utvetydigheter (15-binds vs. *kondenserte*)
% vurderinger på teknikker
% hvorfor er tekniker gruppert slik de er?

@@

%What's the answer? Specifically, most good computer architecture papers
%conclude that something is so many percent faster, cheaper, smaller, or
%otherwise better than something else. Put the result there, in numbers.
%Avoid vague, hand-waving results such as ``very'', ``small'', or
%``significant.''

%If you must be vague, you are only given license to do so when you can
%talk about orders-of-magnitude improvement. There is a tension here in
%that you should not provide numbers that can be easily misinterpreted,
%but on the other hand you don't have room for all the caveats.

% Observation: Kicks happen between stances

@@

%What are the implications of your answer? Is it going to change the
%world (unlikely), be a significant ``win'', be a nice hack, or simply
%serve as a road sign indicating that this path is a waste of time (all
%of the previous results are useful). Are your results general,
%potentially generalizable, or specific to a particular case?

@@

  % Thanks to Master Nicolaisen for pointing out that I allredy had found a
  % problem statement when I was still looking for one
  %
  % Odd-Magne Hansen for helping me with the terminology, and general feedback
  Todo.

@@

    \bibitem{cyclo:con}
      Gen. Choi Hong Hi,
      \emph{Taekwon-Do (the Korean Art of Self-Defence)}, Fifth Edition,
      International Taekwon-Do Federation, 1999.

@@

    \bibitem{golder:ct}
      Scott A. Golder, Bernardo A. Huberman,
      \emph{The Structure of Collaborative Tagging Systems}, 2005.
      \url{http://www.hpl.hp.com/research/scl/papers/tags/tags.pdf}

    \bibitem{heymann:ccch}
      Paul Heymann, Hector Garcia-Molina,
      \emph{Collaborative Creation of Communal Hierarchical Taxonomies in
      Social Tagging Systems}, 2006.
      \url{http://ilpubs.stanford.edu:8090/775/1/2006-10.pdf}

    \bibitem{huang:tt}
      Jeff Huang, Katherine M. Thornton, Efthimis N. Efthimiadis,
      ``Conversational Tagging in Twitter,''
      \emph{Hypertext}, pp. 173-177, 2010.

    \bibitem{jones:folders}
      William Jones, Ammy J. Phuwanartnurak, Rajdeep Gill, Harry Bruce,
      \emph{Don't Take My Folders Away! Organizing Personal Information to Get
      Things Done}, 2005.
      \url{https://dlib.lib.washington.edu/dspace/bitstream/handle/1773/2031/
           Don%27t%20take%20my%20folders%20away%2c%20current.pdf?sequence=2}

    \bibitem{shirky:ontology}
      Clay Shirky,
      \emph{Ontology is Overrated: Categories, Links, and Tags}, 2005.
      \url{http://www.shirky.com/writings/ontology_overrated.html}

    \bibitem{wikipedia:tags}
      \emph{Tag (metadata)}, July 12, 2010. \\
      \url{http://en.wikipedia.org/wiki/Tag}
